# Getting started


```{r setup,echo=FALSE}
suppressMessages({
suppressPackageStartupMessages({
library(BiocStyle)
library(sars2pack)
library(dplyr)
library(ggplot2)
library(tibble)
library(lubridate)
library(DT)
})
})
```

The `r Githubpkg('seandavi/sars2pack')` package uses the [`R statistical programming environment`](https://www.r-project.org/), 
so the first step it to [download and install `R`](https://cloud.r-project.org/). You may also want to _additionally and optionally_ install 
[`Rstudio`](https://rstudio.com/products/rstudio/download/#download). 

## Installation

After installing `R`, from inside the R console, install the `r Githubpkg('seandavi/sars2pack')` package.

```{r eval=FALSE}
install.packages('BiocManager')
BiocManager::install('seandavi/sars2pack')
```

## Usage

To get started using `r Githubpkg('seandavi/sars2pack')`, load the library.


```{r message=FALSE, warning=FALSE, eval=FALSE}
library(sars2pack)
```

The material in this book are located at [extended online book for
documentation](https://seandavi.github.io/sars2pack-book/). 
